Geometric Information for Image Understanding

### 2018-06-06 chapters/introduction/introduction.tex
horizon line introduction.

Lots algorithm focus on extract high-level info from the images. More
and more deep learning algorithm start identifying lower-level info
from the image like edge extracting and vanishing point detection.
(geometric info). Identifying geometric information is useful for many
applications.

>>>>

\brief{Lots algorithm focus on extract high-level info from the images. More
and more deep learning algorithm start identifying lower-level info
from the image like edge extracting and vanishing point detection.
(geometric info). Identifying geometric information is useful for many
applications.}
In computer vision, low-level elements like edges, line segments,
super-pixels and vanishing points play important roles in many
applications like image measuration, facade detection, and
geo-localization.
Though the CNNs are good at extracting high-level information from
images, more and more researches start focusing on using CNN to
extract low-level these elements.

Zhai \etal~\cite{zhai2016horizon} Firstly try to detect horizon
line and vanishing point using global image context extracted by CNN.
Workman \etal~\cite{workman2016horizon} take the idea further and
design an end-to-end network to predict horizon line from images
in the wild. 
Hold-Geoffroy \etal~\cite{hold2017perceptual}
improve~\cite{workman2016horizon}'s results by using deeper networks,
and introduce a new perceptual measure for horizon line detection.
Unlike the previous work that mainly focus on horizon line detection,
Zhang \etal~\cite{zhang2018dominant} propose to detect the dominant
vanishing point using deep neural networks.
